Classify veg

### 2020-11-05 R/classify_species.Rmd
var imp figure formatting

```{r varImp_byWavelength_plot, fig.height=6, fig.width=10}
varImp_MDA_species <- ggplot(imp, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)\n", 
       y = "Variable importance \n",
       title = "Variable Importance: Mean Decrease Accuracy (MDA) \n\nSpecies classification",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca") + 
   theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        title = element_text(size = 16))

@@

Single figure with both variable importance plots:

```{r varmImp_species}
library(ggpubr)

ggpubr::ggarrange(varImp_MDA_species, varImp_Gini_species, nrow = 2)

# save confusion matrix to file 
#ggsave(filename = here::here("analysis","figures", "varImp_species.pdf"), width = 10, height = 10)
```

@@

```{r varImp_MDA_genus, fig.height=6, fig.width=10}
varImp_MDA_genus <- ggplot(imp_genus, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "Wavelength (nm)\n", 
       y = "Variable importance\n",
       title = "Genus classification",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#fc8d59") + 
   theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        title = element_text(size = 16))

>>>>

```{r varImp_byWavelength_plot, fig.height=6, fig.width=10}
varImp_MDA_species <- ggplot(imp, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "",  # x = "Wavelength (nm)\n", # remove x axis label for the combined plot
       y = "Species\nVariable importance\n",
       title = "Variable Importance: Mean Decrease Accuracy (MDA)", # \n\nSpecies classification",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#43a2ca") + 
   theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 16),
        title = element_text(size = 16))

@@

@@

```{r varImp_MDA_genus, fig.height=6, fig.width=10}
varImp_MDA_genus <- ggplot(imp_genus, aes(x=wavelength_nm,  
                y=MeanDecreaseAccuracy)) + 
  # add bars where each height is equal to the variable importance metric
  geom_col(aes(fill = MeanDecreaseAccuracy), color = NA) +
  theme_minimal() + 
  labs(x = "\nWavelength (nm)", 
       y = "Genus\nVariable importance\n",
       #title = "Genus classification",
       fill = "MDA")  + 
  scale_fill_gradient(low = "#d9d9d9", high = "#fc8d59") + 
   theme(axis.text = element_text(size = 14),
        axis.title = element_text(size = 14),
        title = element_text(size = 16))
